Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure

### 2012-05-15 paper.tex
Finished the manuscript for submission

\begin{figure}
  \includegraphics[width=12cm]{initial_treatment.png} 
  \caption{A typical example of the initial treatment of a new sample. After
  performing a light-off ramp, where oscillations can been seen, the temperature
  is increased to a constant value where sustained oscillations take place. The
  non-zero value of CO during high conversion periods is consistent with the
  expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=16cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the
  sample followed by an almost immediate deactivation. For the next 65 minutes
  the sample slowly recovers activity until full conversion is reached again
  and the cycle repeats itself. This extremely long oscillation period is not
  commonly seen and was a result of careful parameter tuning. Typical
  oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
  Inserted circles illustrates the proposed model. At high conversion the
  platinum is oxidized (red) while in low conversion the sample is reduced
  (blue).} \label{fgr:full_oscillation}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=12cm]{summary_of_long_measurement.png}
  \caption{Summary of the oscillation period as a function of time for a sample
  oscillating under constant temperature, pressure and reactant composition.
  The sample went through a total of 439 oscillations in 4 days. For details on on
  the oscillations over this period please consult \ref{fgr:extracts}. Time is
  defined from experiment start and hence includes initial treatment. The inset
  shows the initial steady increase in oscillation period. The red lines indicate
  max and min oscillation time to guide the eye.}
  \label{fgr:long_measurement}
\end{figure}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations
extracted from the same four days measurement. Data from shortly after the
initial treatment, after 2800\,min of oscillation time and after 5900\,min are
shown. After 5900\,min the oscillations are more irregular which is consistent
with the data shown in \ref{fgr:long_measurement}. Also, oscillations in
between full conversion oscillations with smaller amplitude and much higher
frequency than the full on-off cycles become more visible as time progresses.
\begin{figure}
  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from a 4 days long experiment. The oscillation period
  becomes more irregular with time while the total integrated conversion
  remains constant. Furthermore, small oscillations in between full conversion
  cycles become more prominent as time progresses.} \label{fgr:extracts}
\end{figure}

@@

\subsection{Temperature dependence}
\begin{figure}
\includegraphics[width=12cm]{temperature_dependence.png}
\caption{Illustration of the strong temperature dependence of the oscillation period. After about 10
  hours of steady oscillations at 205\,$^\circ$C the temperature is lowered by
  5\,$^\circ$C immediately decreasing the oscillation frequency. The temperature
  is hereafter increased by 2\,$^\circ$C resulting in an increase in oscillation
  frequency. At 205\,$^\circ$C the oscillation period was approximately 500\,s
  while the oscillation period period is approximately 5000\,s. at
  203\,$^\circ$C.
  \label{fgr:temperature_dependence}
}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=12cm]{oscil_gas_dependence_summary.png}
  \caption{Oscillation period (blue) as a function of time and CO concentration (black). The
  overall trend of increasing oscillation period with time is superimposed with small
  discontinuous steps when the CO concentration is increased.} 
  \label{fgr:gas_dependence_summary}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=14cm]{oscil_gas_dependence.png}
  \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$
  (blue). The temperature is constant at $210^\circ$C during the entire
  measurement. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=8cm]{Ib-reactor.png}
 \caption{Image of the 20x16\,mm microreactor showing the circular reactor area
and the gas channel system.}
  \label{fgr:reactor}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=12cm]{initial_treatment.eps} 
  \caption{A typical example of the initial treatment of a new sample. After
  performing a light-off ramp, where oscillations can been seen, the temperature
  is increased to a constant value where sustained oscillations take place. The
  non-zero value of CO during high conversion periods is consistent with the
  expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=16cm]{single_full_oscillation.eps}
  \caption{A full oscillation period first showing a steep ignition of the
  sample followed by an almost immediate deactivation. For the next 65 minutes
  the sample slowly recovers activity until full conversion is reached again
  and the cycle repeats itself. This extremely long oscillation period is not
  commonly seen and was a result of careful parameter tuning. Typical
  oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
  Inserted circles illustrates the proposed model. At high conversion the
  platinum is oxidized (red) while in low conversion the sample is reduced
  (blue).} \label{fgr:full_oscillation}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=12cm]{summary_of_long_measurement.eps}
  \caption{Summary of the oscillation period as a function of time for a sample
  oscillating under constant temperature, pressure and reactant composition.
  The sample went through a total of 439 oscillations in 4 days. For details on on
  the oscillations over this period please consult \ref{fgr:extracts}. Time is
  defined from experiment start and hence includes initial treatment. The inset
  shows the initial steady increase in oscillation period. The red lines indicate
  max and min oscillation time to guide the eye.}
  \label{fgr:long_measurement}
\end{figure}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations
extracted from the same four days measurement. Data from shortly after the
initial treatment, after 2800\,min of oscillation time and after 5900\,min are
shown. After 5900\,min the oscillations are more irregular which is consistent
with the data shown in \ref{fgr:long_measurement}. Also, oscillations in
between full conversion oscillations with smaller amplitude and much higher
frequency than the full on-off cycles become more visible as time progresses.
\begin{figure}
  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.eps}
  \caption{Extracts from a 4 days long experiment. The oscillation period
  becomes more irregular with time while the total integrated conversion
  remains constant. Furthermore, small oscillations in between full conversion
  cycles become more prominent as time progresses.} \label{fgr:extracts}
\end{figure}

@@

\subsection{Temperature dependence}
\begin{figure}
\includegraphics[width=12cm]{temperature_dependence.eps}
\caption{Illustration of the strong temperature dependence of the oscillation period. After about 10
  hours of steady oscillations at 205\,$^\circ$C the temperature is lowered by
  5\,$^\circ$C immediately decreasing the oscillation frequency. The temperature
  is hereafter increased by 2\,$^\circ$C resulting in an increase in oscillation
  frequency. At 205\,$^\circ$C the oscillation period was approximately 500\,s
  while the oscillation period period is approximately 5000\,s. at
  203\,$^\circ$C.
  \label{fgr:temperature_dependence}
}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=12cm]{oscil_gas_dependence_summary.eps}
  \caption{Oscillation period (blue) as a function of time and CO concentration (black). The
  overall trend of increasing oscillation period with time is superimposed with small
  discontinuous steps when the CO concentration is increased.} 
  \label{fgr:gas_dependence_summary}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=14cm]{oscil_gas_dependence.eps}
  \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$
  (blue). The temperature is constant at $210^\circ$C during the entire
  measurement. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=8cm]{reactor.eps}
 \caption{Image of the 20x16\,mm microreactor showing the circular reactor area
and the gas channel system.}
  \label{fgr:reactor}
\end{figure}
